---
title: "linear model from Web"
author: "John Garza"
date: "Spring 2023"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

## Model 1 SIM~ARMS

### scatterplot

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
```

```{r}
basicNN + geom_point() + ggtitle("SIMS vs ARM") + theme(plot.title = element_text(hjust = 0.5, size = 20))
```

The code generated a representation of the data for the relationship between isometric strength tests and job performance for 147 workers. That is why the scatter plot is skewed. Most participant plots landed in the middle with some participants who managed to plot themselves on the outside of the average range.  



### Numerical results
```{r}
cor(SIMS~ARM,data=data)
```
This model is a representation of the correlation between the data. This is why the scatter plot looks the way it looks.

### Inferential  (Build model.1)
```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```
The response from this model is a SIMS value of "-4.095160". This is because the number would represent where a line would cut across the y axis.

#### Predict at target point
```{r}
tgtpoint=data.frame(ARM=88, GRIP=94)
predict(model.1, tgtpoint, interval= c("prediction"))
```

The response from the rcommand predict shows the representation of a 95% prediction interval. That is why the number 0.7063836 is between -1.726209 and 3.138977.

#### scatterplot with model fit
  

## Model 2 SIM~GRIP

### Now add in scatterplot


### Numerical results 


### Inferential  (Build model.2)
  

#### predict model.2 at target point

#### now add the model fit to our plot for model.2
  


## Model 3 SIM~ARM+GRIP

### Numerical results (cor)

`
  
### Inferential  (Build 2-dimentional model.3)

#### predict model.3 at target point
  

## Comparing nested models ANOVA Test

### Model.1 vs Model.3
### Model.2 vs Model.3

## Informally compare Model.1 with model.2

